What Can Stack Traces Tell us about the Use of Exceptions in Java?

### 2014-07-01 android-stacks.tex
including crash/exception information on  Introduction 2

Along the recent years we have witnessed a rapid increase in 
the number of open source software (oss) available on the Web.
Since such projects make their control version system, mailing lists and 
bug tracking systems (bts) publicly available, they represent a valuable 
source of information for the "state of practice" on software development
which has already started to be investigated [][][][][].

@@

Github is also known as a social coding platfotm [ref] as it ....

The bug issues have been the focus of some research... In [ref] defined a 
set of characteristics a good bug issue should have. The 2 most important information 
are the: (1) steps to reproduce the bug; (2) and the failure stack trace.

@@

However, all existing research has focused on the analysis of a single system at a time. In
our current context, on which we have access to wealth of information available
on open-source repositories like GitHub additional questions arise: What are the common
characteristics of such stack traces? Can developers benefit from other systems faults?

>>>>

Along the recent years we have witnessed a rapid increase in 
the number of open source software  available on the Web.
Since such projects make their control version and 
issue tracking systems publicly available, they represent a valuable 
source of information for the "state of practice" on software development
which had already started to be investigated [][][][][].

@@

Among these tools there is the Github issue tracking system, which makes
issues related to new features, improvements, bugs publicly available.

Bug issues have called the attention at have been the target of several 
researchs [][][]. A subtype of a bug issue are the ones related to system 
crashes [complete]...

In [ref] defined a set of characteristics a good bug issue should have. They showed that among 
the most important relevant information are: (1) steps to reproduce the bug; 
(2) and the failure stack trace.

@@

We could observe that existing research has focused on the analysis of a 
single system at a time. Moreover, the search facilities of repositories are very limited, also
enabling the analysis of a single project.

Modern applications have to cope with similar and increasing number of abnormal
computation states that arise as a consequence of faults in the application
itself (e.g., access of null references), noisy user inputs or faults in
underlying middleware or hardware. The exception handling mechanism~\cite{goodenough1975exception} is one of the most used schemes for detecting and recovering from such exceptional conditions.

Although the exception handling mechanism has been embedded in several 
programming languages (e.g. Java, C++, C\#) and was the target of several studies
(e.g.~\cite{miller1997issues,Robil00,shah2010understanding, garcia2007extracting, garcia2001comparative,cabral2007exception,coelho2011unveiling}),
the exception handling code is often generally poorly understood and the least
tested part of software systems.

Specially in the open-source environment, where faults are usualy not hidden in a private trackers,  it would be intresting if developers could learn from other projects mistakes. Moreover, interesting knowledge may emerge from a cross-project crash analysis.

Hence, in such context where we have access to wealth of information available
on open-source repositories such as GitHub, some questions arise: What are the common
characteristics of Github crash reports? How can we benefit from such cross-project crash analysis?

. The ExceptionMiner tool is a contribution in this direction (to enable a cross-project defect analysis).
